A Memory-Bounded, Deterministic and Terminating Semantics for the Synchronous Programming Language~\CEU

### 2018-02-23 02-ceu.tex
Revisão Seção 3-5
Sugestões do Hermann

\CEU is a synchronous reactive language in which programs advance in a sequence
of discrete reactions to external events.
%
It is designed for control-intensive applications, supporting concurrent lines
of execution, known as \emph{trails}, and instantaneous broadcast communication
through events.
%
Computations within a reaction (such as expressions, assignments, and
system calls) are also instantaneous considering the synchronous
hypothesis~\cite{rp.hypothesis}.
%
%\CEU provides an \code{await} statement which is the only that actually
%``consumes'' time.
%
\CEU provides an \code{await} statement that blocks the current running trail
allowing the program to advance its other trails; when all trails are blocked,
the reaction terminates and control returns to the environment.

@@

\subsection{Shared-Memory Concurrency}

>>>>

\CEU is a synchronous reactive language in which programs evolve in a sequence
of discrete reactions to external events.
%
It is designed for control-intensive applications, supporting concurrent lines
of execution, known as \emph{trails}, and instantaneous broadcast communication
through events.
%
Computations within a reaction (such as expressions, assignments, and
system calls) are also instantaneous considering the synchronous
hypothesis~\cite{rp.hypothesis}.
%
%\CEU provides an \code{await} statement which is the only that actually
%``consumes'' time.
%
\CEU provides an \code{await} statement that blocks the current running trail
allowing the program to execute its other trails; when all trails are blocked,
the reaction terminates and control returns to the environment.

@@

\subsection{Shared-Memory Concurrency}
\label{sec.ceu.shared}
